\documentclass{beamer}
%whale
\usetheme{Madrid}
\usecolortheme{whale}

\usepackage{graphicx}

\newenvironment<>{varblock}[2][.9\textwidth]{%
  \setlength{\textwidth}{#1}
  \begin{actionenv}#3%
    \def\insertblocktitle{#2}%
    \par%
    \usebeamertemplate{block begin}}
  {\par%
    \usebeamertemplate{block end}%
  \end{actionenv}}

\setbeamercovered{invisible}

\title{Automatic Committed Belief Tagging}
\author{presented by Chris Hidey}
\institute{Columbia University}

\begin{document}

\frame{\titlepage}

\begin{frame}{Overview}
\begin{enumerate}
\item Background
\item Corpus
\item Methodology
\item Results
\item Critique
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Background}
\begin{block}{Cognitive State}
\begin{itemize}
\item \textbf{Belief }
\item Desire
\item Intention
\end{itemize}
\end{block}

\pause

\begin{block}{Examples}
\begin{itemize}
\item Desire and $\neg$ Belief
\begin{quote}
I know John won't be here but I wouldn't mind if he were
\end{quote}
\pause
\item Belief and $\neg$ Belief
\begin{quote}
\#John won't be here but nevertheless I think he may be here.
\end{quote}
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{Corpus}

10,000 tokens annotated for belief

\begin{block}{Verbal Propositions}
\begin{itemize}
\item Verb
\begin{quote}
Republican leader Bill Frist \textbf{said} the Senate was \textbf{hijacked}.
\end{quote}

\pause

\item Nominal/Adjectival/Prepositional predicate
\begin{quote}
Republican leader Bill Frist \textbf{said} the Senate was \textbf{useless}.
\end{quote}
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{Corpus}
\begin{block}{Belief Tags}
\begin{itemize}
\item Committed belief (CB)
\begin{quote}
GM has laid off workers.
\end{quote}

\pause

\item Non-committed belief (NCB)
\begin{quote}
GM may lay off workers.
\end{quote}

\pause

\item Not applicable (NA)
\begin{quote}
Some wish GM would lay off workers.
\end{quote}

\pause

\item Other (O)
\end{itemize}
\end{block}

\pause

\begin{block}{Subtasks}
\begin{itemize}
\item Identifying propositions (binary classification)
\item Tagging propositions (3-way classification)
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{Methodology}
\begin{block}{Inference}
\begin{itemize}
\item Joint Inference
\begin{itemize}
\item Support Vector Machine (SVM) Chunker
\item Conditional Random Field (CRF)
\end{itemize}
\item Pipeline
\end{itemize}
\end{block}

\pause

\begin{block}{Feature Engineering}
\begin{itemize}
\item Lexical
\item Syntactic
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{Lexical Features}
Derived without parsing
\begin{block}{Informative}
\begin{itemize}
\item numeric
\item POS
\item regular/modal/auxiliary
\end{itemize}
\end{block}
\begin{block}{Uninformative}
\begin{itemize}
\item lemma
\item stem
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{Syntactic Features}
Derived from dependency parse
\begin{block}{Informative}
\begin{itemize}
\item infinitive form
\item reporting ancestor
\item parent POS
\item child
\begin{itemize}
\item perfect tense
\item wh-word
\item auxilary/modal
\end{itemize}
\end{itemize}
\end{block}
\begin{block}{Uninformative}
\begin{itemize}
\item parent lemma/stem
\item supertags
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{Experiments}
\begin{tabular}{|ll|l|l|}
\hline
\multicolumn{4}{|l|}{\textbf{SVM}} \\
\hline
Kernel:& quadratic & \textit{Features} & \textit{F1-score}\\
\cline{3-4}
Slack:& $c=0.5$ & Lexical & 56.9\\
Context Width:& 2 & Lexical and Syntactic & \textbf{64.0}\\
\hline
\end{tabular}

\end{frame}

\begin{frame}{Experiments}
\begin{tabular}{|ll|l|l|}
\hline
\multicolumn{4}{|l|}{\textbf{SVM}} \\
\hline
Kernel:& quadratic & \textit{Features} & \textit{F1-score}\\
\cline{3-4}
Slack:& $c=0.5$ & Lexical & 56.9\\
Context Width:& 2 & Lexical and Syntactic & \textbf{64.0}\\
\hline

%\uncover<+-> {
\multicolumn{4}{l}{\text{}}  \\
\hline 
\multicolumn{4}{|l|}{\textbf{CRF}} \\
\hline 
Order:& 1 & \textit{Features} & \textit{F1-score} \\
\cline{3-4} 
Gaussian Variance:& 1 & Lexical & 49.6 \\
& & Lexical and Syntactic & 59.0 \\
\hline 
%}
\end{tabular}
\end{frame}

\begin{frame}{Experiments}
\begin{tabular}{|ll|l|l|}
\hline
\multicolumn{4}{|l|}{\textbf{SVM}} \\
\hline
Kernel:& quadratic & \textit{Features} & \textit{F1-score}\\
\cline{3-4}
Slack:& $c=0.5$ & Lexical & 56.9\\
Context Width:& 2 & Lexical and Syntactic & \textbf{64.0}\\
\hline

%\uncover<+-> {
\multicolumn{4}{l}{\text{}}  \\
\hline 
\multicolumn{4}{|l|}{\textbf{CRF}} \\
\hline 
Order:& 1 & \textit{Features} & \textit{F1-score} \\
\cline{3-4} 
Gaussian Variance:& 1 & Lexical & 49.6 \\
& & Lexical and Syntactic & 59.0 \\
\hline 
%}

\multicolumn{4}{l}{\text{}} \\
\hline
\multicolumn{4}{|l|}{\textbf{Pipeline}} \\
\hline
SVM binary tagger & & \textit{Features} & \textit{F1-score}\\
\cline{3-4}
Context Width:& 2 & Lexical and Syntactic & 46.1\\
\cline{3-4}
\multicolumn{2}{|l}{SVM 3-way classifier} & \multicolumn{2}{l|}{\text{}} \\
\multicolumn{2}{|l}{trained on gold data} & \multicolumn{2}{l|}{\text{}} \\
\hline

\end{tabular}

\end{frame}

\begin{frame}{Critique}
\begin{itemize}
\item Clarity?
\begin{itemize}
\item Well-written and understandable
\item More explanation of features and parameters
%discussion of dataset (unbalanced)
\item Confusion matrix or error analysis
\end{itemize}

\pause

\item Methodology/Evaluation?
\begin{itemize}
\item Additional baselines
%lemma/stem baseline
\item Training/testing
\item Statistical significance
\end{itemize}
%Impact?

\pause
\item Originality?

\pause

\item Reproducibility?
\begin{itemize}
\item Depends on code and data availability
\item Parameter tuning
\item Training/evaluation/testing
\end{itemize}

\pause
\item Impact?

\end{itemize}
\end{frame}

\begin{frame}{Critique}
\begin{itemize}
\item Positives?
\begin{itemize}
\item Well-defined problem, high IAA
\item Not too domain-specific
\item Comparison of pipeline versus joint inference
\end{itemize}

\pause

\item Negatives?
\begin{itemize}
\item Requires dependency parsing
\item Language-specific
\end{itemize}
\end{itemize}

\end{frame}

\end{document}
